\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.3in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{array}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\renewcommand{\labelitemi}{\textbullet}
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=1pt, parsep=0pt, partopsep=0pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}
  \begin{tabularx}{\textwidth}{Xr}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabularx}\vspace{-3pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{1pt}
  \begin{tabularx}{\textwidth}{Xr}
    \textbf{#1} & #2 \\
  \end{tabularx}\vspace{-3pt}
}

\begin{document}

\begin{center}
    {\LARGE \textbf{Musa Abdulrafiu}}\\
    615-484-2718 $|$ \href{https://www.linkedin.com/in/musa-abdulrafiu}{LinkedIn} $|$ \href{mailto:Musaabdulrafiu20@gmail.com}{Musaabdulrafiu20@gmail.com} $|$ \href{https://github.com/MMAbdul153}{GitHub}
\end{center}

\section*{Education}
\resumeSubheading
{Fisk University} {\textbf{Nashville, TN}}
{Bachelor of Science in Computer Science} {Expected Graduation: May 2027}
\resumeItemListStart
    \item Relevant Coursework: Data Structures and Algorithms, Computer Organization, Calculus I \& II
    \item Honors/Awards: Erastus Milo Cravath Presidential Scholarship (\$138,000)
\resumeItemListEnd

\section*{Technical Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Programming Languages:} & Python, Java, C++, JavaScript, TypeScript, Kotlin \\
\textbf{Web \& Mobile Development:} & React, React Native, Angular, Node.js, HTML, CSS \\
\textbf{Backend \& Databases:} & Express.js, PostgreSQL, MongoDB, Firebase (Auth, Firestore, Cloud Functions), Redis \\
\textbf{Cloud \& Infrastructure:} & AWS (EC2, S3, Lambda, API Gateway, CloudWatch), Docker, CI/CD, Linux/Unix \\
\textbf{Software Engineering:} & OOP/OOD, Design Patterns, Distributed Systems, SDLC, Microservices \\
\textbf{Tools \& Technologies:} & Git, REST APIs, Jest, Jasmine, Karma \\
\end{tabularx}

\section*{Experience}
\resumeSubheading
{Google Inc.} {\textbf{San Francisco, CA}}
{Associate Software Developer Intern} {May 2025 -- August 2025}
\resumeItemListStart
    \item Built and launched the Experiment Hover Card for Primes UI using Angular and TypeScript, reducing experiment discovery time by 40\%.
    \item Developed the feature from skeleton component to full functionality, including rollout support, error handling, and loading/empty states, reducing UI failure occurrences by 30\%.
    %\item Added an Experiment Extension badge to improve filter accuracy as part of the Product Excellence initiative.
    \item Used metrics and logs to guide feature decisions and validate performance improvements.
    \item Wrote 100+ unit and integration tests with Jasmine/Karma, increasing component coverage from 78\% to 96\%.
\resumeItemListEnd

\resumeSubheading
{Fisk University Department of Computer Science} {\textbf{Nashville, TN}}
{AI/ML and Cyber-Physical Power Systems Security Research Intern} {June 2024 -- August 2024}
\resumeItemListStart
    \item Applied supervised learning techniques, including CNNs, to analyze 27 videos and 40,000 frames from U.S. Department of Energy data for defect detection in pressure vessels and superheaters.
    \item Built a deep learning pipeline in Python using TensorFlow InceptionV3 for transfer learning and OpenCV for automated image processing.
    \item Integrated Stochastic Gradient Descent (SGD), achieving 99.47\% accuracy even in challenging detection cases.
\resumeItemListEnd

\section*{Projects}
\resumeProjectHeading
{FiskConnect - Full-Stack Mobile Application}{React Native, Firebase, Firestore, Expo, React Navigation, Git}
\resumeItemListStart
    \item Built a campus-only mobile application for Fisk University students, restricting access to verified \texttt{@fisk.edu} accounts to create a trusted peer-to-peer marketplace and task coordination platform.
    \item Integrated Firebase Authentication, Cloud Firestore, and real-time \texttt{onSnapshot} listeners to deliver live updates for listings, tasks, and messages in 1--2 seconds without manual refresh.
    \item Designed secure Firestore data models and access rules for users, listings, tasks, conversations, and nested message threads; validated functionality across both Android and iOS devices.
\resumeItemListEnd

\resumeProjectHeading
{ArtisanConnect - E-Marketplace for Handmade Goods} {React, Node.js, Express.js, PostgreSQL, REST APIs, Git}
\resumeItemListStart
    \item Architecting a scalable marketplace connecting U.S. buyers with global artisans selling handmade shoes, outfits, and custom products.
    \item Designed a PostgreSQL schema to support 1,000+ products, user accounts, order flows, and future platform growth.
    \item Built REST APIs with Node.js and Express for catalog management, user dashboards, and product interactions.
    \item Developed a responsive React front end for both desktop and mobile users, improving usability and accessibility.
    \item Leveraged Generative AI tools such as ChatGPT, Gemini, and Claude for test case generation, debugging, and faster iteration.
\resumeItemListEnd

\resumeProjectHeading
{Finna Walk - Full-Stack Mobile App} {React Native, Node.js, MongoDB, Firebase}
\resumeItemListStart
    \item Built a full-stack fitness networking app enabling real-time student matching and session scheduling.
    \item Applied React Native concepts, including prop-based data transfer, useState, and useEffect, with collaborative development through Git.
    \item Applied OOP principles and modular component design across frontend and backend layers.
    \item Used Firebase Auth, Cloud Functions, Firestore, and security rules to authenticate users and securely manage student data.
\resumeItemListEnd

\section*{Extracurriculars}
\resumeItemListStart
    \item Fisk University Carl Van Vechten Gallery Ambassador.
\resumeItemListEnd

\end{document}